A Realistic Guide to Making Data Available Alongside Code to Improve Reproducibility

### 2019-09-09 paper.Rmd
add some more detail on analysis vs raw data, remove some details on SDSS data

1. README
2. Data dictionary
3. License
4. Citation
5. Analysis ready data

@@

The data used in the data analysis should be provided in a folder called `data`. Ideally, the data should be in "Tidy Data" format [@Wickham2014], where tidy data contains variables in columns, and observations in rows. Contrasting "raw data", "analysis ready data" should be in an easily readable plain-text format, such as CSV, tab separated, or semicolon separated. Binary or proprietary formats are discouraged in favor of interoperability, as it requires special software to read, even if it is sometimes slower to read in and out, and harder to share due to size.

@@

Metadata from the data cannot be contained in the CSV file, but is available in the URL the csv was downloaded from: `http://dr15.sdss.org/optical/spectrum/view/data/format=csv?`
`plateid=1678&mjd=53433&fiberid=425&reduction2d=v5_7_0`

Which contains details of the data, specifically:

* plateid = 1678
* mjd = 53433
* fiberid = 425
* reduction2d = v5.7.0

These are unique identifying features of the data, which tell us:

* **plateid:** the unique plate used to explore a given section of night sky. 
* **mjd:** an integer that marks the "modified julian date" of the night of observation.
* **fiberid:** an integer of the fiber optic cable used to transmit light to the sensor.
* The **version** marked as `v5_7_0` is the pipeline version used for BOSS in DR12.

As a researcher who does not work in astrophysics, this information on the data was quite easy to retrieve from the SDSS website section called "Understanding SDSS spectroscopic data": https://www.sdss.org/dr12/spectro/spectro_basics/.

>>>>

1. README
2. Data dictionary
3. License
4. Citation
5. Analysis ready data
6. Scripts to tidy analysis raw data into ready data

@@

The data used in the data analysis should be provided in a folder called `data`. Ideally, the data should be in "Tidy Data" format [@Wickham2014], where tidy data contains variables in columns, observations in rows, and only one value per cell.

In contrast to "raw data", "analysis ready data" should be in an easily readable plain-text format, such as comma-, tab- or semicolon-separated. Binary or proprietary formats are discouraged in favor of interoperability, as it requires special software to read, even if it is sometimes slower to read in and out, and harder to share due to size. There are times where Tidy Data format can inflate the size of data due to repetition, which make it difficult to share - in these cases it might be worthwhile to consider multiple smaller, connected tables or other easily compressible formats such as apache Arrow.

@@
